### 2021-10-28 paper/pldi22/formal.tex
Target function / abstract arguments in static analysis

To define static analysis of $\ires$ programs, we first define abstract domains
of states, calling contexts, environments, and values as follows:
\begin{itemize}
  \item \underline{Abstract States}:
    $\aelemset = \actxtset \times \afsenvset$
    \[
      \begin{array}{lcl}
        \gamma(\afsenv, \actxt) &=& \gamma(\actxt) \cap
        \gamma(\afsenv)\\

@@

  \item \underline{Abstract Calling Contexts}:
    $\actxtset = \funcset \finmap \powerset{\labset \times \varset}$
    \[
      \todo
      \begin{array}{lcl}
        \gamma(\actxt) &=& \{ \st \in \stset \mid
          \st = (\lab', (\lab, \_, \varx) :: \_, \_, \_) \wedge \\&&
          \phantom{\{ \st \in \stset \mid} (\lab, \varx) \in
            \actxt(\getfunc(\lab'))
        \}\\

>>>>

To define static analysis of $\ires$ programs, we first define target function
and its abstract arguments based on a given syntactic view $\atree$.  Since only
non-leaf nodes has single evaluation functions, we assume that $\atree = \ty_k
\langle \atree_1, \cdots, \atree_n \rangle$.  Then, the target function and its
abstract arguments are defined as follows:
\[
  \begin{array}{ll@{~}c@{~}l}
    \text{Target Function} & \targetfunc &=& \ty_k.\eval\\

    \text{Abstract Arguments} &
    [\aval_0, \cdots, \aval_m] &=&
    [\atree, \atree_{i_1}, \cdots, \atree_{i_m}]\\
  \end{array}
\]
where $m$ denotes the number of nonterminal subtrees of $\atree$ and
$\atree_{i_j}$ denotes $j$-th one for each $1 \leq i \leq m$.  The abstract
domains of states, calling contexts, environments, and values are defined as
follows:
\begin{itemize}
  \item \underline{Abstract States}:
    $\aelemset = \actxtset \times \afsenvset$
    \[
      \begin{array}{lcl}
        \gamma(\afsenv, \actxt) &=& \gamma(\actxt) \cap
        \gamma(\afsenv)\\

@@

  \item \todo \underline{Abstract Calling Contexts}:
    % \powerset{\labset \times \funcset}
    $\actxtset = \funcset \finmap \powerset{\labset \times \varset}$
    \[
      \begin{array}{lcl}
        \gamma(\actxt) &=& \{ \st \in \stset \mid
          \st = (\lab', (\lab, \_, \varx) :: \_, \_, \_) \wedge \\&&
          \phantom{\{ \st \in \stset \mid} (\lab, \varx) \in
            \actxt(\getfunc(\lab'))
        \}\\
